### 2021-11-11 NSF2021/Description/specificaim2.tex
removed domain fig in SA1

\label{subsec:specific_aim_2}
\begin{wrapfigure}[14]{r}{0.61\textwidth}
  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
    \vspace{-15pt}
    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
    amphiphilic particles suspended in a solvent. The solvent velocity
    satisfies the Stokes equations, and the hydrophobic forces depend on
    the solvent activity that satisfies the screened Laplace equation.
    The geometry is updated by solving the mobility problem.} 
\end{wrapfigure}
The HAP model requires solving exterior Dirichlet problems for the order
parameter~\eqref{eq:SL} and the Stokes
equations~\eqref{eq:stokes1}--\eqref{eq:stokes3}. If discretizing these
equations with stencil-based numerical methods, the computational domain
must be truncated, the fluid volume must be discretized, and artificial
boundary conditions must be imposed. The artificial boundary conditions
introduce additional error, and discretizing the volume results in an
excessively large system of equations. Moreover, it is difficult to
obtain high-order discretizations when the boundary surfaces are
irregular.

>>>>

%\label{subsec:specific_aim_2}
%\begin{wrapfigure}[14]{r}{0.61\textwidth}
%  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
%    \vspace{-15pt}
%    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
%    amphiphilic particles suspended in a solvent. The solvent velocity
%    satisfies the Stokes equations, and the hydrophobic forces depend on
%    the solvent activity that satisfies the screened Laplace equation.
%    The geometry is updated by solving the mobility problem.} 
%\end{wrapfigure}
The HAP model requires solving exterior Dirichlet problems for the order
parameter~\eqref{eq:SL} and the Stokes
equations~\eqref{eq:stokes1}--\eqref{eq:stokes3}. If discretizing these
equations with stencil-based numerical methods, the computational domain
must be truncated, the fluid volume must be discretized, and artificial
boundary conditions must be imposed. The artificial boundary conditions
introduce additional error, and discretizing the volume results in an
excessively large system of equations. Moreover, it is difficult to
obtain high-order discretizations when the boundary surfaces are
irregular.
